An examination of the high-order dynamic interactions underlying multi-dimensional timeseries data

### 2019-03-27 paper/main.tex
corrected some minor formatting things

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/methods_fig}
  \caption{\textbf{Computing higher order correlations. } Correlations
  are computed then approximated to the same size as original data.
  This process is repeated to computer }
  \label{fig:methods_fig}
\end{figure}

@@

For each order we obtained the weighted-mixture of the correlation
matrices for the current order and all previous orders using mixing parameter , $\phi$, where $0 <\phi< 1$ reflects a
weighted mixture of order based decoding Fig.~\ref{fig:decode_level}
Panel C. ). We calculated  $\phi$, by
subdividing the training group and using the quasi-Newton method of
Broyden, Fletcher, Goldfarb, and Shanno (BFGS) for optimization. We
repeated this cross-validation process 100 times.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figs/methods_fig}
  \caption{\textbf{Computing higher order correlations. } Correlations
  are computed then approximated to the same size as original data.
  This process is repeated to computer }
  \label{fig:methods_fig}
\end{figure}

@@

For each order we obtained the weighted-mixture of the correlation
matrices for the current order and all previous orders using mixing parameter , $\phi$, where $0 <\phi< 1$ reflects a
weighted mixture of order based decoding Fig.~\ref{fig:decoding_level}
Panel C. ). We calculated  $\phi$, by
subdividing the training group and using the quasi-Newton method of
Broyden, Fletcher, Goldfarb, and Shanno (BFGS) for optimization. We
repeated this cross-validation process 100 times.
